---
title: "EDA"
output: html_document
---

Run setup:

```{r}
source("setup/run_setup.R")
```

```{r}
summary(mv_data)
```

What does it mean that "N_claims_year" does not sum to "N_claim_history":
```{r}
mv_data %>% filter(ID == 39)
```

```{r}
ID_claim_sus <- mv_data %>% 
  group_by(ID) %>% 
  summarise(
    N_claims_year_sum = sum(N_claims_year),
    N_claims_history = max(N_claims_history),
    is_decreasing = all(diff(N_claims_year) <= 0)
  ) %>% 
  filter(
    N_claims_year_sum > N_claims_history
  )
```

```{r}
ID_claim_sus %>% filter(is_decreasing == FALSE)
```

```{r}
mv_data %>% filter(ID == 39) %>% select(ID, Date_last_renewal, Date_next_renewal,Cost_claims_year, N_claims_year, N_claims_history) %>% xtable()
```

All examples of sum(N_claims_year) > N_claims_history
```{r}
mv_data %>% 
  filter(ID %in% ID_claim_sus[["ID"]]) %>% 
  select(ID, N_claims_year, N_claims_history,Cost_claims_year, Date_last_renewal, Date_lapse)
```


What does it mean that a contract is terminated on the same day it is renewed, and that Cost_claims_year > 0
```{r}
mv_data_tmp %>% 
  filter(Date_last_renewal == Date_lapse) %>% 
  filter(Cost_claims_year > 0) %>% 
  select(ID, Date_last_renewal, Date_lapse, Cost_claims_year, N_claims_year)
```

```{r}
mv_data_tmp %>% 
  filter(Date_next_renewal == Date_lapse) %>% 
  select(Date_next_renewal, Date_lapse, Cost_claims_year, N_claims_year)
```


How is the Cost_claims_year calculated?
```{r}
mv_data %>% 
  filter(ID == 263) %>% 
  select(ID, Date_last_renewal, Date_lapse, Cost_claims_year, N_claims_year, N_claims_history)
```
It cannot be due to a lag of N_claims_history being updated, since:
```{r}
mv_data %>% 
  filter(N_claims_history < N_claims_year)
```



Type_risk has a lot to say about length and Type_fuel are NA, which makes sense:

```{r}
mv_data %>%
  group_by(Type_risk) %>%
  summarise(
    n = n(),
    NA_Length = sum(is.na(Length)),
    NA_Type_fuel = sum(is.na(Type_fuel)),
    NA_Distrubution_channel = sum(is.na(Distribution_channel)),
    freq = mean(N_claims_year),
    avg_claim = sum(Cost_claims_year) / sum(N_claims_year),
  )
```
```{r}
mv_data %>% 
  filter(Type_risk == "Agricultural vehicles" & Length > 0) %>% # (Type_risk == "Motorbikes")
  select(ID, Type_risk, Length)
```


```{r}
mv_data %>% 
  group_by(Type_fuel, Type_risk) %>% 
  summarise(n=n())
```

```{r}
mv_data %>% 
  group_by(Type_risk, Distribution_channel) %>% 
  summarise(n=n())
```


Check if the exposure variable is valid?:
```{r}
mv_data_tmp %>% 
  mutate(
    Exposure_type = case_when(
      Exposure < 0 ~ "<0",
      Exposure == 0 ~ "0",
      0 < Exposure & Exposure < 1 ~ "(0,1)",
      Exposure == 1 ~ "1",
      Exposure > 1 ~ ">1"
    )
  ) %>% 
  group_by(Exposure_type) %>%
  summarise(
    # freq = sum(N_claims_year)/sum(Exposure),
    n = n(),
    total_claim = sum(Cost_claims_year),
    total_claim_N = sum(N_claims_year),
  ) %>% arrange(total_claim) 
```
```{r}
mv_data_tmp %>% 
  filter(Date_last_renewal == Date_lapse)
```


```{r}
mv_data_tmp %>% 
  filter(Exposure > 1)
```


Removing all rows, with negative exposure. Where contract is terminated before renewal date:
```{r}
mv_data %>% 
  filter(Exposure < 0) %>% 
  select(Date_last_renewal, Date_lapse)

# mv_data <- mv_data %>%
#   filter(Exposure >= 0)
```

```{r}
mv_data %>% filter(0 < Exposure & Exposure < 1) %>% select(Date_last_renewal, Date_lapse)
```
We now handle the three columns with mussing values
  - We see that mast Motorbikes are Petrol, and Agricultural vehicles are Diesel. 
  - Since problem with MB and AG, and correlated with weight for the others.
  - We inpute missing in distrubution_channel with and "other category
```{r}
mv_data_imp <- mv_data %>%
  mutate(
    Type_fuel = case_when(
      Type_risk == "Agricultural vehicles" & is.na(Type_fuel) ~ "Diesel",
      Type_risk == "Motorbikes" & is.na(Type_fuel) ~ "Petrol",
      TRUE ~ Type_fuel,
      .ptype = Type_fuel
    )
  ) %>%
  select(-Length, -Date_next_renewal, -Lapse, -Date_lapse) %>%
  mutate(Distribution_channel = fct_na_value_to_level(Distribution_channel, "other"))
```


